\chapter{Survey Design}
\label{surveyDesign}
The experimental design of RadGrad includes three steps: a baseline assessment, a post-deployment assessment, and a final comparison between the two. These assessments will be given to current undergraduate ICS students and prospective ICS students. It will be deployed electronically via Google Forms and prospective ICS students will be given the assessment during their initial advising session. Current ICS students will be given the assessment during any voluntary advising session and also voluntarily through their ICS courses. Ideally, at least 50 responses will be gathered for both assessments.
\section{Baseline Assessment}
\label{baselineAssessment}
	The baseline assessment will contain the following questions. The full assessment can be found in Appendix A. 

\subsection{Basic Information}
\begin{enumerate}
\item \textit{What is your gender? }
Goal: Since the ICS program currently has significantly more male students than female students, what are are the differences between the experiences of the two genders? Could this give any insight into why there are so little female students? Is this something RadGrad could address? After implementing RadGrad, have there been any differences in the gender ratio or the disparity between the experiences of the two genders? Ideally, both genders should have equally positive experiences in the ICS program.
\item \textit{What is your current status in the ICS degree program?}
Goal: How do student experiences evolve as they progress through the ICS degree program? Are there any patterns? Does RadGrad have any effect on this? Ideally, students from all levels should have equally positive experiences in the ICS program. 
\end{enumerate}

\subsection{Prospective ICS Students}
\begin{enumerate}
\item\textit{ How EXCITED are you about entering the ICS program? Rank from 1-5.}
Goal: Compare this answer to the same question on the post-deployment assessment.  This will provide information regarding how students view the ICS department, based solely on outside information and before their own experiences. Ideally, RadGrad will create more excitement among prospective students due to better presentation and the appearance of a strong, supportive community and satisfied alumni.
\item \textit{How INTIMIDATED do you feel about entering the ICS program? Rank from 1-5.}
Goal: Compare this answer to the same question on the post-deployment assessment.  This will provide information regarding how students view the ICS department, based solely on outside information and before their own experiences. Ideally, RadGrad will create less intimidation among prospective students due to the appearance of a strong, supportive, and diverse community and satisfied alumni. 
\end{enumerate}

\subsection{Current ICS Students}
\begin{enumerate}
\item \textit{Which of the following extracurricular activities, if any, pertain to you? }
Goal: Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will increase the amount of student involvement in outside ICS-related activities due to providing students with stronger connections to the ICS community.
\item \textit{Do you feel that you get enough support from others in the ICS department?}
Goal: Are students lacking support in certain areas? How can RadGrad help to address this? Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will provide a way to give more students the support they desire from others in the department. 
\item \textit{As a student, do you feel like you have a voice to make changes within the department?}
Goal: If most students indicate that they do not feel like they have a voice within the department, what can RadGrad do to address this problem? Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will cause more students to feel like they do have a voice to make changes in the department.
\item \textit{What makes you proud to be a part of the ICS department?}
Goal: This provides information about how current students view the department. A successful department should have a positive reputation among students, which can be manifested with a sense of pride. Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will cause positive changes in the ICS department's reputation, leading to a greater sense of pride among students, which may play a role in students' success
\end{enumerate}

\subsection{Current ICS Students: Influences}
\begin{enumerate}
\item \textit{To what extent have ICS alumni influenced your development in the ICS program?}
Goal: Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will facilitate more student-alumni interaction, and cause more students to be influenced in some way by an alumn in an ICS-related way.
\item \textit{To what extent have ICS peers influenced your development in the ICS program?}
Goal: Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will facilitate more peer interaction, and cause more students to be influenced in some way by a peer in an ICS-related way.
\item \textit{To what extent have you influenced your ICS peers’ development in the ICS program?}
Goal: Compare this answer to the same question on the post-deployment assessment. Ideally, RadGrad will facilitate more peer interaction, and cause more students play a role in influencing their peers in an ICS-related way.
\end{enumerate}

\subsection{Graduating ICS Students}
\begin{enumerate}
\item \textit{Now that you are nearing the end of your ICS degree program experience, how well prepared do you feel to find a job after graduation?}
Goal: If the ICS department is fulfilling its duty, most graduating students should feel at least adequately prepared (ideally well prepared) for the future. If most students indicate that they do not feel prepared, what can RadGrad do to address this problem? Ideally, after deploying RadGrad, a higher percentage of students will feel either adequately prepared or well prepared for the future.
\item \textit{If you answered above that you feel unprepared to find a job after graduation, please explain why. }
Goal: Are there any common reasons for students not feeling prepared? If so, is there anything RadGrad can do to address this problem? Ideally, after deploying RadGrad, there will be a lower percentage of students who indicate the same problems as the preliminary questionnaire. 
\end{enumerate}

\section{Post-Deployment Assessment}
The post-deployment assessment has not yet been created, and will be created after deploying RadGrad. A section of the post-deployment assessment will contain the same questions as the preliminary assessment, with some additional choices where necessary to include RadGrad. Another section of the post-deployment assessment will contain questions specific to the student's reactions to using different aspects of RadGrad. In addition to the assessment, post-deployment analysis will include data from at least 10 interviews with RadGrad users to get more detailed information about the users' experiences.

\section{Comparison}
After all results of both assessments have been collected (ideally 50 each), they will be compared regarding student expectations versus reality, student satisfaction with the department, student engagement, and student feelings. The overall goal of RadGrad is to see suggestions of positive changes between the preliminary questionnaire and a post-deployment questionnaire that reflect less disparity between student expectations and reality, greater student satisfaction with the department, more student engagement, and more positive student feelings. These changes will support the hypothesis that RadGrad could cause several significant and positive changes with the students of the ICS department.